Figures

### 2019-05-10 figures/06_lulc_buffer_demo.Rmd
add stream buffer satellite pics

```{r buffer-lulc_vs_iws-lulc, echo=FALSE}
dt <- readRDS("../data/dt.rds") %>%
  mutate(diff = stream_cultivated_crops - ag_pct) %>%
  drop_na(diff)

ggplot(data = dt) +
  geom_point(aes(x = ag_pct, y = stream_cultivated_crops, color = diff > 3)) +
  geom_abline(aes(slope = 1, intercept = 0)) +
  theme(legend.position = 0)
# 
# res_pnt  <- query_gis("LAGOS_NE_All_Lakes_4ha_POINTS", "lagoslakeid", 
#                       dplyr::filter(dt, diff > 0)$lagoslakeid)
res_iws  <- query_gis("IWS", "lagoslakeid", 
                      dplyr::filter(dt, diff > 3)$lagoslakeid)

@@

i <- 7
r_raw      <- images_sized[[i]]
r          <- projectRaster(r_raw, crs = as.character(st_crs(s))[2])

>>>>

```{r buffer-lulc_vs_iws-lulc, echo=FALSE, fig.height=3}
dt <- readRDS("../data/dt.rds") %>%
  mutate(diff = stream_cultivated_crops - ag_pct) %>%
  drop_na(diff)

ggplot(data = dt) +
  geom_point(aes(x = ag_pct, y = stream_cultivated_crops, color = diff > 3)) +
  geom_abline(aes(slope = 1, intercept = 0)) +
  theme(legend.position = 0)
```

```{r satellite, echo=FALSE}
# 
# res_pnt  <- query_gis("LAGOS_NE_All_Lakes_4ha_POINTS", "lagoslakeid", 
#                       dplyr::filter(dt, diff > 0)$lagoslakeid)
res_iws  <- query_gis("IWS", "lagoslakeid", 
                      dplyr::filter(dt, diff > 3)$lagoslakeid)

@@

i          <- 7
s          <- res_iws[iws_sized[i],]
r_raw      <- images_sized[[i]]
r          <- projectRaster(r_raw, crs = as.character(st_crs(s))[2])

### 2019-05-10 manuscript/figures.Rmd
add stream buffer satellite pics

>>>>

```{r lulc_vs_iws-lulc, fig.cap = "Stream buffer versus IWS lulc.", warning=FALSE, echo = FALSE}
knitr::include_graphics("../figures/buffer-lulc_vs_iws-lulc-1.pdf")
```

```{r big_stream_ag, fig.cap = "Stream buffer Ag >> IWS", warning=FALSE, echo = FALSE}
knitr::include_graphics("../figures/satellite-1.pdf")
```

```{r small_stream_ag, fig.cap = "Stream buffer Ag << IWS", warning=FALSE, echo = FALSE}
knitr::include_graphics("../figures/satellite-2.pdf")
```
